```{r include=F}
1 + 1
```

---
title: "Concepts & Objectives"
---

## Concepts

How CSS Works with HTML together?

-   Connection & Location
-   CSS Style Rules
-   CSS Property name & value

CSS associates HTML `elements` with `style rules` using `selector`.

> A selector is a string pattern which searches all the matching elements by their html tags and attributes.

Some types of identifiers used in *naming a selector*:

-   HTML `element TAG`
-   `CLASS` attribute can be applied to more than one html elements.
-   `ID` attribute should only be applied to one element.

## Naming Convention

For maximum compatibility, you must comply with the following naming rules:

-   Always begin a selector name with a letter.
-   Do not use any blank spaces.
-   Use letters, numbers, dash and underscore.

## Case-sensitivity

**CLASS and ID selectors in CSS are case-sensitive.**

## CSS Syntax Validator

Use the following W3C's CSS validator *https://jigsaw.w3.org/css-validator/* to help you identify syntax errors.

```{r echo=FALSE, include=F, eval=F}
knitr::include_url("https://jigsaw.w3.org/css-validator/")
```

## Objectives

A Web designer must master CSS technology and has an ability of reading, applying, creating and updating CSS for Web pages.

-   Embed a style block inside the `<head>` element using `<style>` tag
-   Add (ad-hoc) `inline style` within an element using `style attribute`
-   Read and write CSS rules
-   Use several types of selectors: `element name`, `class`, `id`, and `descendant selector`
-   Know a web browser runs a selector as a string pattern to find all the matching HTML elements on a Page and apply the rules to the elements.
-   Associate/link an `external CSS` script with an HTML page using `<link>` tag within the head element:

```{html filename="link_to_external_css"}
<head>
<link rel="stylesheet" href="{path.to.css.file}">
</link>
</head>
```

-   Debug CSS and tune style sheets for its associated HTML (using VS Code)

-   Look up resources including color code, element tags, css property names, css selector syntax, HTML code for special symbols and entities.
