```{r include=F}
1 + 1
```

---
title: List, Image, Figure, Picture
---

## Text Pages

::: callout-tip
### Text Pages

```{r out.height = "460px", out.width='600px', echo=F}
knitr::include_graphics("file/text_ch5-css-others.pdf")
```
:::

## CSS List Marker 

::: {.callout-important}
#### Try-it-yourself CSS List Markers

https://www.w3schools.com/css/css_list.asp
:::





## Image Styling

::: callout-note
#### Try-it-yourself CSS Image Styling Properties

https://www.w3schools.com/html/html_images.asp
:::

## HTML Image Map

::: callout-note
#### Try-it-yourself Image Map

https://www.w3schools.com/html/html_images_imagemap.asp
:::

## HTML figure & figcaption

::: callout-note
#### Try-it-yourself HTML Figure Element

https://www.w3schools.com/tags/tag_figure.asp
:::

## HTML Favicon

::: callout-note
#### Try-it-yourself HTML Favicon

https://www.w3schools.com/html/html_favicon.asp
:::


## HTML picture Element

::: callout-note
#### Try-it-yourself HTML Picture Element

https://www.w3schools.com/html/html_images_picture.asp
:::
