---
title: "Yoga-3"
---


::: {.callout-tip}
### Yoga-3 Incorporate images & Focus on Page Design

Use Resort-3 as a template, **Pacific Trails Resort Chapter 5 folder**. Use Yoga-2 as a starting point to create Yoga-3 by incorporating the following updates: 

- Display a large image on each page
- Create a new Activities page
:::


## The Page Layout 

```{mermaid}
graph TB
    a(1)-->w1; b(3)-->w1; c(10)-->w1;
    w1-->|average|a1[4.666667];
    d(3)-->w2; e(5)-->w2; f(7)-->w2;
    w2-->|average|a2[5];
    g(9)-->w3; h(6)-->w3; i(5)-->w3;
    w3-->|average|a3[6.666667];
    a1-->s1[average of every k numbers];a2-->s1;a3-->s1;
    style w1 fill:#80deb2,stroke:#333,stroke-width:2px
    style w2 fill:#80deb2,stroke:#333,stroke-width:2px
    style w3 fill:#80deb2,stroke:#333,stroke-width:2px
    style s1 fill:#e4c9b4,stroke:#333,stroke-width:2px  

```

##

To start the work, watch the following video.

```{r, eval=knitr::is_html_output(excludes = "epub"), results = 'asis', echo = F}
cat(
'<iframe width="560" height="315" src="https://www.youtube.com/embed/iCjabFr3GR4" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>'
)
```





## Resort-3

Click **Show files button** to open the file pane.

```{r, eval=knitr::is_html_output(excludes = "epub"), results = 'asis', echo = F}
cat(
'<iframe frameborder="0" width="100%" height="500px" src="https://replit.com/@Jager2021/resort-2?embed=true"></iframe>'
)
```


## Requirements 

Follow the instructions on pages -.


  Upload (Yoga-2) Chapter 4 folder to your remote Web account


**Relevant Text Pages**

```{r out.height = "460px", out.width='600px', echo=F}
knitr::include_graphics("file/text_yoga-2.pdf")
```



