---
title: "Yoga-2"
---

Use Resort-2 as a template, **Pacific Trails Resort Chapter 4 folder**. Add CSS to the last version Yoga-1.

To start the work, watch the following video.

```{r, eval=knitr::is_html_output(excludes = "epub"), results = 'asis', echo = F}
cat(
'<iframe width="560" height="315" src="https://www.youtube.com/embed/iCjabFr3GR4" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>'
)
```





## Resort-2

Click **Show files button** to open the file pane.

```{r, eval=knitr::is_html_output(excludes = "epub"), results = 'asis', echo = F}
cat(
'<iframe frameborder="0" width="100%" height="500px" src="https://replit.com/@Jager2021/resort-2?embed=true"></iframe>'
)
```


## Requirements 

Follow the instructions on pages 265-.

1.  Create a style sheet script: **yoga.css**
2.  Link the script to both existing pages: index.html and classes.html
3.  Upload (Yoga-2) Chapter 4 folder to your remote Web account


**Relevant Text Pages**

```{r out.height = "460px", out.width='600px', echo=F}
knitr::include_graphics("file/text_yoga-2.pdf")
```



